---
title: "Attrition Analyis"
author: "Connor Dobbs"
date: "11/14/2021"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    theme: united
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.width = 10, 
                      fig.asp = 0.618, 
                      out.width = "80%", 
                      fig.align = "center", 
                      message = FALSE, 
                      warning = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(skimr)
library(GGally)
library(viridis)
library(corrplot)
library(glue)
library(class)
library(caret)
library(e1071)
```

# Introduction: 

#### The CEO AND CFO have tasked outside consultant Connor Dobbs to investigate Employee Attrition and Income trends.

#### With the rising importance of employee rentention in the current labor market, there have been a few specific goals outlined for this research to help minimize attrition and maintain Frito-Lay's strong talent pool.

 1. Identify the three most important factors associated with attrition
 1. Identify the most important factors associated with employee income
 1. Identify any other potentially useful trends or patterns within the data
 1. Develop a model to predict employee attrition
 1. Develop a model to predict Monthly Income
 
 

#### This investigation finds strong trends with age, job role, and overtime status leading to attrition that can be focused on moving forward to improve rention. A full conclusion summary with recommendations is at the end of the document and can be skipped to via the table of contents to the left. 

---

## Tools used

#### Human Resources has kindly provided the dataset to be used for this analysis. Data visulizations were used to explore the data and relationships within it. 

#### Statistical methods used include: KNN classification, linear regression, and Naive-Bayes classification

#### Additional questions about the results can be directed towards Connor Dobbs via e-mail: dobbs@smu.edu

##### *Note, all code chunks are hidden by default. There is an option to the right of each chunk to expand/collapse. You can also expand/collapse all with the Code button on the top right of this document.

---

# Initial Steps:

Begin by loading the data and initial cleaning. There is no missing values which is good, however there are some variables that appear to be of no use to be removed.
```{r}
#load in hr data
hrdf <- read.csv('Data/CaseStudy2-data.csv')

#check for NA, get familiar with distributions
skim(hrdf)

# Changing the datatype to factors for relevant variables
cols <- c("Education", "EnvironmentSatisfaction", "JobInvolvement", "JobLevel",
         "JobSatisfaction", "PerformanceRating", "RelationshipSatisfaction", 
         "StockOptionLevel", "TrainingTimesLastYear", "WorkLifeBalance", 
         "Attrition", "BusinessTravel", "Department", "EducationField", 
         "Gender", "JobRole", "MaritalStatus", "Over18", "OverTime")

hrdf[cols] <- lapply(hrdf[cols], factor)

#remove variables that add should add no info unless leakage (employee count, etc.)
hrdf <- subset(hrdf, select = -c(EmployeeCount, EmployeeNumber, Over18, StandardHours))

```

---

#### Quick overview of attrition distribution - It appears to be fairly unbalanced, with only 16% of the data a "yes".

```{r}
#plot attrition - unbalanced data with only 16% yes
hrdf %>% ggplot(aes(x = Attrition, fill = Attrition)) + geom_bar() + 
  theme_stata() + ggtitle("Employee Attrition (Count)") + ylab("Employee Count") +
    scale_fill_stata()

hrdf %>% group_by(Attrition) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
  ggplot(aes(x = Attrition, y = pct, fill = Attrition)) + geom_bar(stat = 'identity') + 
  theme_stata() + ggtitle("Employee Attrition (%)") + ylab("Attrition %") +
  geom_text(aes(x=Attrition, y=0.01, label= sprintf("%.2f%%", pct)),
            hjust=0.5, vjust=-3, size=4, 
            colour="black", fontface="bold") + labs(x="Employee Attrition", y="Percentage") +
    scale_fill_stata()
```

---

### Create Functions for EDA

```{r}
bar_plot_check <- function(x, y){
  
  x <- enquo(x)
  y <- enquo(y)
  varName <- as_label(enquo(x))
  varName <- str_to_title(str_replace(varName, "Group", ""))
  
  plot1 <- hrdf %>% group_by(!!x) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
    ggplot(aes(x = !!x, y = count, fill = !!x)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
    theme_stata() + ggtitle(glue("{varName} Distribution")) + ylab("Count") +
    geom_text(aes(x = !!x, y=0.01, label= sprintf("%.2f%%", pct)),
              hjust=0.5, vjust=-3, size=4, position = position_dodge(0.9),
              colour="black", fontface="bold") + labs(x =glue("{varName}"), y="Count") +
      scale_fill_stata()
  
  plot2 <-
    hrdf %>% group_by(!!x, !!y) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
    ggplot(aes(x = !!x, y = pct, fill = !!y)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
    theme_stata() + ggtitle(glue("Attrition % by {varName}")) + ylab("Attrition %") +
    geom_text(aes(x = !!x, y=0.01, label= sprintf("%.2f%%", pct)),
              hjust=0.5, vjust=-3, size=4, position = position_dodge(0.9),
              colour="black", fontface="bold") + labs(x =glue("{varName}"), y="Attrition %") +
      scale_fill_stata()

  print(plot1)
  print(plot2)
}


box_plot_check <- function(x, y, title){
  
  x <- enquo(x)
  y <- enquo(y)
  varName <- as_label(enquo(x))
  varName <- str_to_title(str_replace(varName, "Group", ""))
  
  plot <- hrdf %>%
    ggplot(aes(x = !!y, y = !!x, fill = !!y)) + geom_boxplot(alpha = .7) + 
    geom_jitter(color = 'black', size = .4) +
    theme_stata() + ggtitle(title) + ylab(glue("{varName}")) +
      scale_fill_stata()
  
  print(plot)
}

```

---

# Exploratory Data Analysis:


### Income

* Higher income seems to be associated with less attrition.
```{r}
#income - higher income seems to be less associated with less attrition
hrdf %>% select(Attrition, MonthlyIncome) %>% group_by(Attrition) %>% skim()

box_plot_check(MonthlyIncome, Attrition, "Monthly Income by Attrition")
```

---


### Travel 

* Fairly unbalanced, most people in "travel rarely" category, but those who travel frequently quit at higher rate - as expected.
```{r}
hrdf %>% group_by(BusinessTravel) %>% summarize(count = n())

bar_plot_check(BusinessTravel, Attrition)
```

---

### Distance from home 

* Higher distance appears related to more attrition, but no visual evidence of strong relationship, more variance with attrition.
```{r}
hrdf %>% select(Attrition, DistanceFromHome) %>% group_by(Attrition) %>% skim()

box_plot_check(DistanceFromHome, Attrition, "Distance from Home by Attrition")
```

---

### Education 

* Low # of level five education, that does not appear to be much different attrition than level 4, so grouping together for a potential increase in degrees of freedom. 

* Higher education has less attrition, probably correlated with income, etc. 

* Education field has unbalanced distributions, so while HR field has the highest attrition rate, with a count of 15, it is probably not a very accurate measure to use.
```{r}
hrdf %>% group_by(Education) %>% summarize(count = n())

bar_plot_check(Education, Attrition)

#grouping 4 and 5 together
hrdf$GroupEducation <- ifelse(hrdf$Education %in% c(4,5), "4+",
                              hrdf$Education)

bar_plot_check(GroupEducation, Attrition)

hrdf %>% group_by(EducationField) %>% summarize(count = n())

bar_plot_check(EducationField, Attrition)
```

---

### Age

* Grouping into factor, taking into account distribution but also intuition about ages of "early career". Attrition seems to decrease as age increases, with the 25 and under bracket leaving at significantly higher rates than others. Age also correlated with income.
```{r}
summary(hrdf$Age)

box_plot_check(Age, Attrition, "Age")

hrdf$GroupAge = cut(hrdf$Age, breaks = c(-1, 25.1, 35.1, 45.1, 100), labels = c("18-25","26-35","35-45","46+"))

bar_plot_check(GroupAge, Attrition)
```

---

### Department + Job Role Trends

* Department Trend
    + Highest turnover in Sales Dpt, lowest in R&D. 
    + Correlates well with Job Roles, with Sales Reps having almost 50% turnover. 

* Job Role Trends
    + Income
        - As expected, leadership (non-manager) monthly income is the highest
        - Interestingly, Healthcare Representatives income is in line with Sales Executives and Manufacturing Directors in a "middle" income bracket
        - These middle brackets appear to also have the highest variance
    + Job Satisfaction
        - Manager satisfaction tends to be lowest, with the highest % in the 1 and 2 buckets
        - Research Scientists tend to be the most satisfied, with the least % in the 1 and 2
        - Sales Executives have some of the highest % with a 4 rating, but also a high 1 rating %
    + Work Life Balance
        - Trends appear fairly similar across all groups with leadership tending slightly towards worse balance and sales reps having the most "middle ground"
    + Environment Satisfaction
        - Fairly consistent, except with Research Directors and managers liking their environments the least
        
```{r}
hrdf %>% group_by(Department) %>% summarize(count = n())
hrdf %>% group_by(JobRole) %>% summarize(count = n())

bar_plot_check(Department, Attrition)

  hrdf %>% group_by(JobRole) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
    ggplot(aes(x = JobRole, y = count, fill = JobRole)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
    theme_stata() + ggtitle(glue("Job Role Distribution")) + ylab("Count") +
    geom_text(aes(x = JobRole, y=0.01, label= sprintf("%.2f%%", pct)),
              hjust=0.5, vjust=-3, size=4, position = position_dodge(0.9),
              colour="black", fontface="bold") + labs(x = 'Job Role', y="Count") +
      scale_fill_stata() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
  hrdf %>% group_by(JobRole, Attrition) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
    ggplot(aes(x = JobRole, y = pct, fill = Attrition)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
    theme_stata() + ggtitle(glue("Attrition % by Job Role")) + ylab("Attrition %") +
    geom_text(aes(x = JobRole, y=0.01, label= sprintf("%.2f%%", pct)),
              hjust=0.5, vjust=-3, size=3, position = position_dodge(0.9),
              colour="black", fontface="bold") + labs(x = 'Job Role', y="Attrition %") +
      scale_fill_stata() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
  
jobdf <- hrdf %>% select(JobRole, JobSatisfaction, WorkLifeBalance, MonthlyIncome, EnvironmentSatisfaction, GroupEducation)

jobdf %>% ggplot(aes(x = MonthlyIncome, fill = reorder(JobRole, MonthlyIncome, mean))) + geom_boxplot() +
  theme_stata() + scale_fill_stata() + ggtitle("Income Distribution by Role") + guides(fill=guide_legend(title="Job Role"))

jobdf %>% group_by(JobRole, JobSatisfaction) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
  ggplot(aes(x = JobSatisfaction, y = pct, fill = JobRole)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
  theme_stata() + ggtitle(glue("Job Satisfaction % by Job Role")) + ylab("Satisfaction %") + facet_wrap(~JobRole) + scale_fill_stata()

jobdf %>% group_by(JobRole, WorkLifeBalance) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
  ggplot(aes(x = WorkLifeBalance, y = pct, fill = JobRole)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
  theme_stata() + ggtitle(glue("Work Life Balance % by Job Role")) + ylab("Work Life Balance %") + facet_wrap(~JobRole) + scale_fill_stata()

jobdf %>% group_by(JobRole, EnvironmentSatisfaction) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
  ggplot(aes(x =EnvironmentSatisfaction, y = pct, fill = JobRole)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
  theme_stata() + ggtitle(glue("Environment Satisfaction % by Job Role")) + ylab("Environment Satisfaction %") + facet_wrap(~JobRole) + scale_fill_stata()

jobdf %>% group_by(JobRole, GroupEducation) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
  ggplot(aes(x = GroupEducation, y = pct, fill = JobRole)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
  theme_stata() + ggtitle(glue("Education % by Job Role")) + ylab("Education %") + facet_wrap(~JobRole) + scale_fill_stata()
```

---

### Gender + Marital Status

* Males have a slightly higher turnover rate, however not very significant.

* Marital status on the other hand shows that Single people have a much higher turnover than Married or Divorced people
    + Gender does not make a large difference here either. 
```{r}
bar_plot_check(Gender, Attrition)
bar_plot_check(MaritalStatus, Attrition)

  hrdf %>% group_by(Gender, MaritalStatus, Attrition) %>% summarize(count = n()) %>% mutate(pct=round(prop.table(count),2) * 100) %>%
    ggplot(aes(x = Gender, y = pct, fill = Attrition)) + geom_bar(stat = 'identity', position = 'dodge', alpha = .7) + 
    theme_stata() + ggtitle(glue("Attrition % by Job Role")) + ylab("Attrition %") +
    geom_text(aes(x = Gender, y=0.01, label= sprintf("%.2f%%", pct)),
              hjust=0.5, vjust=-3, size=3, position = position_dodge(0.9),
              colour="black", fontface="bold") + labs(x = 'Gender', y="Attrition %") +
      scale_fill_stata() + facet_wrap(~MaritalStatus)
```

---

### Rates

* It is unclear what these are, however they do not appear strongly related to each other or have consistent trends with Attrition. 
* Due to a lack of explainability, these will be left out of any further analysis unless a better understanding of what these represent is provided
    + Including in analysis causes risk since it is hard to say if there are any potential data integrity issues with the distributions

```{r}
#ggally with rates to get a better idea what relationship is or is not
hrdf %>% select(DailyRate, HourlyRate, MonthlyRate, MonthlyIncome, Attrition) %>% ggpairs()

box_plot_check(HourlyRate, Attrition, "Hourly Rate by Attrition")

box_plot_check(DailyRate, Attrition, "Daily Rate by Attrition")

box_plot_check(MonthlyRate, Attrition, "Monthly Rate by Attrition")

```

---

### Satisfaction

* Environment satisfaction appears to have consistent turnover at a rating of 2 or more. Those with a rating of 1 have quite a higher turnover.

* Job satisfaction has a more downward trend at each level, and those with a 4 have significantly less turnover than the other 3 ratings.

* Relationship satisfaction has a less consistent trend, although those with a rating of 1 have a more significant turnover than the other 3. 

* Low work life balance has more than double turnover rate than other groups, fairly low count though. Job Involvement has similar pattern.
```{r}
bar_plot_check(EnvironmentSatisfaction, Attrition)

bar_plot_check(JobSatisfaction, Attrition)

bar_plot_check(RelationshipSatisfaction, Attrition)

bar_plot_check(WorkLifeBalance, Attrition)

bar_plot_check(JobInvolvement, Attrition)
```

---

### Time Variables

* More time with current manager correlated with less attrition, probably related with both manager and job satisfaction. 

* Time since last promotion does not have any strong visual trends.

* Years in current role and years spent at company correlated with less attrition, similar to time with current manager

* More variance in number of companies worked for those who quit, probably related to age of employees with higher turnover but who also haven't had experience to be at more than 1 company. 

```{r}
box_plot_check(YearsWithCurrManager, Attrition, "Years with current Mgr by Attrition")

box_plot_check(YearsSinceLastPromotion, Attrition, "Years since last promotion by Attrition")

box_plot_check(YearsInCurrentRole, Attrition, "Years in current role by Attrition")

box_plot_check(YearsAtCompany, Attrition, "Years spent at company by Attrition")

box_plot_check(NumCompaniesWorked, Attrition, "Total # of Companies worked by Attrition")
```

---

### Other Variables

* Most employees at level 0 or 1. Interestingly highest turnover occurs at 0 (expected) but also at the highest level 3. 

* Not a strong difference in the only two levels found of performance rating (3 and 4). 

* Non-exempt employees (overtime = yes) with triple the turnover than exempt. 

```{r}
bar_plot_check(StockOptionLevel, Attrition)

bar_plot_check(PerformanceRating, Attrition)

bar_plot_check(OverTime, Attrition)
```

---

### Monthly Income Relationships

* By Department
    + Sales have highest median income
    + R&D have highest incomes observed
    + HR has most variation but also lowest median
    
* By Job Level
    + Each job level is correlated with an increase in income, as expected

* Attrition Significance
    + P value < .001 that log Monthly Income is different between those who stay and leave

```{r}
hrdf %>% ggplot(aes(x = Department, y = MonthlyIncome, fill = Department)) +
  geom_boxplot(alpha = .7) + geom_hline(aes(yintercept = median(MonthlyIncome), color = 'red')) +
  theme_stata() + scale_fill_stata()

hrdf %>% ggplot(aes(x = JobLevel, y = MonthlyIncome, fill = JobLevel)) +
  geom_boxplot(alpha = .7) + geom_hline(aes(yintercept = median(MonthlyIncome), color = 'red')) +
  theme_stata() + scale_fill_stata()

hrdf$logIncome <- log(hrdf$MonthlyIncome)
t.test(logIncome ~ Attrition, data = hrdf)
```

---

### Correlation Check

* Nothing too unexpected

* Total Working Years strong correlation with Monthly Income, Age, and other "time" variables

* "Rate" variables not strongly correlated, as mentioned earlier
```{r}
#cor testing
nums <- select_if(hrdf, is.numeric)

corr <- round(cor(nums), 1)

corrplot(corr, 
           type = "lower",
           method="number")
```

---


# Attrition Prediction:

## KNN

### Feature Selection

* The following variables were removed for redundancy or lack of usefullness:
    + ID
    + Age
    + Education

* The following variables were removed due to lack of explainability/trust in data:
    + HourlyRate
    + DailyRate
    + MonthlyRate
    
### Feature Manipulation

The data was centered and scaled. The scaling is particularly important for Income, as otherwise it could be at risk of being overly weighted in importance.

### Method and Results

* Repeated K-fold cross validation was used, with 75% data splits and 100 repetitions of 5 folds. 

* The model was set at maximizing specificity, as this is the hardest variable to maximize here, and potentially the most important (identifying attrition risks that retention efforts could be spent on)

* Sensitivity (correctly prediction no attrition) of 88% was achieved

* Specificity (correct predictions of attrition) of 80% was achieved. 


```{r}
set.seed(44)

cleandf <- subset(hrdf, select = -c(DailyRate, HourlyRate, MonthlyRate, ID, Age, Education))

# control settings for KNN
# NOTE: needed in order to focus on specificity

train.knn <- trainControl(
  method = "repeatedcv",
  number = 5,
  repeats = 100,
  summaryFunction = twoClassSummary,
  classProbs = TRUE,
  p = .75
)

# KNN on Training Set

attrition.knn <- train(
  Attrition ~ .,
  data = cleandf,
  method = "knn",
  metric = "Spec",
  trControl = train.knn,
  preProcess = c("center","scale"),
  tuneLength = 6
)

# Adding predictions to df
cleandf$KNN_Pred <- predict(attrition.knn, newdata = cleandf)
# creating confusion matrix
confusionMatrix(table(cleandf$Attrition, cleandf$KNN_Pred))
```

---

## Naive-Bayes

### Feature Selection

* The same variables used with the KNN were used here for similar assumptions
    
### Feature Manipulation

Monthly Income was replaced with the log of Monthly Income to help get closer to a normal distribution. 

### Method and Results

* With 100 repeats of 75% splits
    + Sensitivity hovered around 90-91%
    + Specificity struggled around ~55%. 



```{r}
cleandf$logIncome <- log(cleandf$MonthlyIncome)

cleandf2 <- subset(cleandf,select = -c(KNN_Pred, MonthlyIncome))

iterations = 100
masterAcc = matrix(nrow = iterations)
masterSens = matrix(nrow = iterations)
masterSpec = matrix(nrow = iterations)

for(j in 1:iterations)
{
    
  trainIndices = sample(seq(1:length(cleandf2$Attrition)),round(.75*length(cleandf2$Attrition)))
  trainNaive = cleandf2[trainIndices,]
  testNaive = cleandf2[-trainIndices,]
  
  model = naiveBayes(trainNaive[,-1], trainNaive$Attrition)
  CM = confusionMatrix(table(predict(model,testNaive[,-1]), testNaive$Attrition))
  masterAcc[j] = CM$overall[1]
  masterSens[j] = CM$byClass[1]
  masterSpec[j] = CM$byClass[2]
}

MeanAcc = colMeans(masterAcc)
MeanSens <- colMeans(masterSens)
MeanSpec <- colMeans(masterSpec)

MeanAcc
MeanSens
MeanSpec

```

---


# Monthly Income Prediction:

## Linear Regression

### Feature Selection

* Started with same "cleaned" variables at the Naive Bayes Attrition Model
    + Fitted a model with all variables to determine which were most significant based off P-values and test statistics
    + Narrowed this list down to just the following 4 most important variables to improve degrees of freedom and prevent over fitting with too many variables
        - Total Working Years
        - Job Role
        - Job Level
        - Business Travel
        
    + These variables also make intuitive sense, as most organizations operate with "salary bands" for given roles based on type, level, and employee experience. 
    
### Feature Manipulation

No further manipulation was needed. The residual plots and QQ plots looked good for assumptions of linearity. There is some caution of departure from normality at the upper level of incomes, where we have seen data to be the most skewed and present of outliers. Log fitting for income did not help improve this fit. 

### Method and Results

* The four variables mentioned above were able to predict Monthly Income with an RMSE of only $993.

* Variables ordered by importance based off test statistics:
    + Job Level
    + Job Role
    + Total Working Years
    + Business Travel


* An Adjusted R squared of .95 infers that 95% of the variability in Monthly Income can be explained by these 4 variables. 

```{r}
cleandf3 <- subset(cleandf,select = -c(KNN_Pred))

fit <- lm(MonthlyIncome ~ ., data = cleandf3)
summary(fit)

fit2 <- lm(MonthlyIncome ~ TotalWorkingYears + JobRole + JobLevel + BusinessTravel, data = cleandf3)

summary(fit2)

#check assumptions, violation of normality at upper bounds, otherwise great
par(mfrow = c(2, 2))
plot(fit2)

```

```{r class.source = 'fold-show'}
#calculate RMSE
sqrt(mean(fit2$residuals^2))
```



# Conclusion:

#### In summary, we derived the following insights from our analysis:

 1. Identify the three most important factors associated with attrition:
    + **OverTime** - Non-Exempt employees with Overtime have a 32% attrition rate, double the average.
    + **Age** - Attrition rates are much higher the younger a person is, particularly for those in the 18-25 early career bracket which has a 33% attrition rate.
    + **Job** Role - In particular, Sales Reps have an astounding 45% turnover rate
 1. Identify the most important factors associated with employee income:
    + **Job Level**
    + **Job Role**
    + **Total Working Years**
 1. Develop a model to predict employee attrition:
    + Our best performing model (KNN) was able to predict:
        - Sensitivity (Identifying those who do not leave) with **88%** success.
        - Specificity (Identifying those who do leave) with **80%** success. 
    + The overall model's accuracy could be higher, however this model is optimized for identifying attrition risks with as much success as possible.
    + A Naive-Bayes model was able to have slightly better accuracy, but failed to get a specificity higher than about 55%, below our required threshold. 
 1. Develop a model to predict Monthly Income:
    + Our best performing model (linear regression) was able to predict income with an RMSE of less than **$1000**. 
 1. Identify any other potentially useful trends or patterns within the data:
      + Income
          - As expected, leadership (non-manager) monthly income is the highest
          - Interestingly, Healthcare Representatives income is in line with Sales Executives and Manufacturing Directors in a "middle" income bracket
          - These middle brackets appear to also have the highest variance
     + Job Satisfaction
         - Manager satisfaction tends to be lowest, with the highest % in the 1 and 2 buckets
         - Research Scientists tend to be the most satisfied, with the least % in the 1 and 2
         - Sales Executives have some of the highest % with a 4 rating, but also a high 1 rating %
      + Work Life Balance
          - Trends appear fairly similar across all groups with leadership tending slightly towards worse balance and sales reps having the most "middle ground"
      + Environment Satisfaction
         - Fairly consistent, except with Research Directors and managers liking their environments the least
    
#### Based on these insights we have the following recommendations that Frito-Lay can explore in further detail:

 1. A follow up investigation is necessary to understand what is leading to the high turnover for some job roles, particularly Sales Rep, and what can be done to improve retention.
 1. Focus on general retention strategies for younger employees - an authentically ethical and inclusive company culture, work life balance flexibility, and skill growth tend to be rated as more important for this age group compared to others (https://hbr.org/2020/06/what-your-youngest-employees-need-most-right-now, data trends from Pew Research Center). 
 1. Income is a strong predictor of turnover as well, it could be worth looking into better identifying top performers and making sure that their Job Level and potentially Role/Title can be improved as necessary, without being as restricted by age or total experience. 
 1. The KNN model can be used to identify employees that could potentially be at a higher risk of turnover to focus efforts on.
 
